HPC--101 -- Cheatsheet \vspace{-2ex}

### 2016-01-22 hpc_101/cheatsheet/paper.tex
update to some wording in a few command description

\section{Modules}
\begin{itemize}
\item[] \texttt{module avail} \desc{List all available software modules}
\item[] \texttt{module load \pth{module name}} \desc{Load the specified module into your environment}
\item[] \texttt{module show \pth{module name}} \desc{Shows you what actions the module performs to your environment}
\item[] \texttt{module purge} \desc{unload all loaded modules}
\end{itemize}

\section{Miscellaneous}
\subsection{Commands}
\begin{itemize}
\item[] \texttt{less \pth{file}} \desc{Show contents of file\\Navigate using up/down arrow keys, spacebar, or pageup/pagedown keys\\Press 'q' to exit out of less}
\item[] \texttt{less -S \pth{file}} \desc{Show contents of file without line wrap\\Navigate using up/down arrow keys, spacebar, or pageup/pagedown keys\\Press 'q' to exit out of less}
\item[] \texttt{man \pth{command}} \desc{Show the manual entry (if one exists) for the given command\\Press 'q' to exit out of less}
\end{itemize}

>>>>

\section{Modules}
\begin{itemize}
\item[] \texttt{module avail} \desc{List all available software modules}
\item[] \texttt{module load \pth{module name}} \desc{Load the specified module into your environment}
\item[] \texttt{module show \pth{module name}} \desc{Shows you what actions the module performs on your environment}
\item[] \texttt{module purge} \desc{unload all loaded modules}
\end{itemize}

\section{Miscellaneous}
\subsection{Commands}
\begin{itemize}
\item[] \texttt{less \pth{file}} \desc{Show contents of file\\Navigate using up/down arrow keys, or spacebar\\Press 'q' to exit out of less}
\item[] \texttt{less -S \pth{file}} \desc{Show contents of file without line wrap\\Navigate using up/down arrow keys, or spacebar\\Press 'q' to exit out of less}
\item[] \texttt{man \pth{command}} \desc{Show the manual entry (if one exists) for the given command\\Uses the same controls as less\\Press 'q' to exit out of man}
\end{itemize}
